---
title: "Proportion of red beads"
format: html


---



```{r}
library(tidymodels)
library(broom)

title: "Distribution of Ball Colors in the Urn"
format: html
editor: visual
---

## Exploring the Urn

This chart shows how often each color appears in the urn.

```{r}
library(tidyverse)

# Create example urn data if not already defined
urn <- tibble(
  color = sample(c("red", "blue"), size = 1000, replace = TRUE, prob = c(0.3, 0.7))
)

# Plot
ggplot(urn, aes(x = color, fill = color)) +
  geom_bar(width = 0.6, alpha = 0.9, color = "black") +
  labs(
    title = "Frequency of Red and Blue Balls in the Urn",
    subtitle = "Blue balls are more common in this simulated urn sample",
    x = "Ball Color",
    y = "Count",
    caption = "Simulated Data for Demonstration"
  ) +
  scale_fill_manual(values = c("red" = "#e74c3c", "blue" = "#3498db")) +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(face = "bold", size = 18),
    plot.subtitle = element_text(size = 14),
    legend.position = "none"
  )
```
